---
title: "Analysis of SARS-CoV-2 concentration in wastewater"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 2
params:
  state: "nj"
  download_raw_data: FALSE
hitheme: tomorrow
highlighter: highlight.js
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)

knitr::opts_chunk$set(echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 9,
  fig.height = 6,
  fig.path = "../results/"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```


# Overview

```{r, include = FALSE}
download_date = Sys.Date()
```


This file produces a report of the wastewater concentration of SARS-CoV-2 in different counties in `r toupper(params$state)`. Data for this report was downloaded from the CDC website on `r download_date`.

# Download and clean data

Two data sources were pulled and merged for this analysis. One is a dataset of SARS-CoV-2 wastewater concentration at different sampling sites, which can be accessed [here](https://data.cdc.gov/Public-Health-Surveillance/NWSS-Public-SARS-CoV-2-Concentration-in-Wastewater/g653-rqe2/about_data). The second, accessible [here](https://data.cdc.gov/Public-Health-Surveillance/NWSS-Public-SARS-CoV-2-Wastewater-Metric-Data/2ew6-ywp6/about_data), contains summary information about SARS-CoV-2 wastewater concentration at different sites, with additional information about site location including county and state.

First we downloaded and cleaned the data from the CDC website. 

```{r}
if(params$download_raw_data){
  source(here("source", "01_data_download.R")) 
}else if(!file.exists(here::here("data", "raw.Rdata"))){
  source(here("source", "01_data_download.R")) 
}

source(here("source", "02_data_cleaning.R")) 
```


# Analysis

Next we did a simple analysis of the concentrations across different counties in `r toupper(params$state)`. Specifically, we calculated the median and interquartile range within each county, which are given in the table below:

```{r}
source(here("source", "03_data_analysis.R"))
```

```{r}
covid_table %>%
  knitr::kable()
```





# Visualization

Finally, we visualize the concentration across counties. 

```{r}
source(here("source", "04_data_visualization.R"))
```

First we look at boxplots of the `log(concentration)` of SARS-CoV-2 across counties in `r toupper(params$state)`. The counties have been shorted from lowest to highest SARS-CoV-2 concentration.

```{r, figure1}
plot1
```


Next, we visualize trends in SARS-CoV-2 concentration over time.

```{r, figure2, fig.height = 10}
plot2
```


